---
title: "Introduction to TCMC"
author: 
  - name: Dany Mukesha
    affiliation:
    - Université Côte d'Azur
    email: danymukesha@gmail.com
output: 
  BiocStyle::html_document:
    self_contained: yes
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: show
date: "`r doc_date()`"
package: "`r pkg_ver('TCMC')`"
vignette: >
  %\VignetteIndexEntry{Introduction to TCMC}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}  
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    crop = NULL ## Related to https://stat.ethz.ch/pipermail/bioc-devel/2020-April/016656.html
)
```


```{r vignetteSetup, echo=FALSE, message=FALSE, warning = FALSE}
startTime <- Sys.time()
library("RefManageR")
bib <- c(
    R = citation(),
    BiocStyle = citation("BiocStyle")[1],
    knitr = citation("knitr")[1],
    RefManageR = citation("RefManageR")[1],
    rmarkdown = citation("rmarkdown")[1],
    sessioninfo = citation("sessioninfo")[1],
    testthat = citation("testthat")[1],
    TCMC = citation("TCMC")[1]
)
```

# Basics

## Install `TCMC`

`r Biocpkg("TCMC")` will be be soon available on [Bioconductor](http://bioconductor.org). 

```{r "install", eval = FALSE}
if (!requireNamespace("BiocManager", quietly = TRUE)) {
    install.packages("BiocManager")
}
BiocManager::install("TCMC")
BiocManager::valid()
```

## Citing `TCMC`

I hope that `r Biocpkg("TCMC")` will be useful for research. 
Please use the following information to cite the package 
and the overall approach. Thank you!

```{r "citation"}
citation("TCMC")
```

# Quick start to using `TCMC`

```{r "start", message=FALSE}
library("TCMC")
```

```{r usage, eval=FALSE}
data(PimaIndiansDiabetes)

results <- compare_models(PimaIndiansDiabetes, "diabetes")

# access trained models
best_model <- results$trained_models$gbm

# plot variable importance for a specific model
plot_importance(results$trained_models$lvq, "LVQ")
```


Here is an example of you can cite your package inside the vignette:

* `r Biocpkg("TCMC")` `r Citep(bib[["TCMC"]])`

Date the vignette was generated.

```{r reproduce1, echo=FALSE}
Sys.time()
```

Wallclock time spent generating the vignette.

```{r reproduce2, echo=FALSE}
totalTime <- diff(c(startTime, Sys.time()))
round(totalTime, digits = 3)
```

`R` session information.

```{r reproduce3, echo=FALSE}
library("sessioninfo")
options(width = 120)
session_info()
```

# Bibliography

```{r vignetteBiblio, results = "asis", echo = FALSE, warning = FALSE, message = FALSE}
PrintBibliography(bib, .opts = list(hyperlink = "to.doc", style = "html"))
```
